Safe Shared Memory for Concurrent Algol

### 2017-10-12 proposal.tex
typo

We plan to create a language building on the ideas of \LangCA{} which has primitive concepts for concurrency, shared memory, and locking.
Our intent is that this language will disallow writing programs with certain classes of errors ranging from the relatively minor (For example, memory leaks or multiple acquisition of the same lock) to more complex ones including data races (potentially with some restrictions) and deadlocks.

>>>>

We plan to create a language building on the ideas of \LangCA{} which has primitive concepts for concurrency, shared memory, and locking.
Our intent is that this language will disallow writing programs with certain classes of errors ranging from the relatively minor (for example, memory leaks or multiple acquisition of the same lock) to more complex ones including data races (potentially with some restrictions) and deadlocks.
